---
title: "Tasks 1 & 2: Interactive plots"
toc: true
---

## Task 1: Session check-in

Three interesting or exciting things:

1. Learning how to turn regular ggplots into interactive plots using Plotly.
2. Seeing how tooltips can display custom information when hovering over points.
3. Understanding how to combine multiple variables into one label.

Three muddy or unclear things:

1. How to format tooltip labels correctly without getting confused by paste/glue.
2. When to use aes versus putting arguments outside of it.
3. How shapes and colors are assigned automatically versus manually.

---

## Task 2: Interactive plot

```{r}
library(tidyverse)
library(plotly)

# Technically this isn't necessary; you can run `penguins` and start using it 
# right away since it's a core dataset. This code just puts the dataset in the 
# environment panel so it's easier to see what's in there.
penguins <- datasets::penguins

# 11 rows are missing data on penguin sex, so we drop them
penguins <- penguins |> 
  drop_na(sex)
```

```{r}
penguins <- penguins |> 
  mutate(
    label = paste0(
      species, " (", sex, " on ", island, ")\n",
      "Bill depth: ", round(bill_dep, 1), " mm\n",
      "Bill length: ", round(bill_len, 1), " mm"
    )
  )


```

```{r}
head(penguins$label)

```

```{r}
penguin_plot <- ggplot(
  penguins,
  aes(
    x = bill_len,
    y = bill_dep,
    color = species,
    shape = species,
    text = label
  )
) +
  geom_point(size = 3) +
  scale_color_manual(values = c("darkorange", "purple", "cyan4")) +
  theme_light() +
  labs(
    x = "Bill length (mm)",
    y = "Bill depth (mm)",
    color = "Species",
    shape = "Species"
  )

penguin_plot

```

```{r}
ggplotly(penguin_plot, tooltip = "text")

```

